Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Edits to final proofs of abstain-half in appendix

	If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$. 
	WLOG, these points from top left to top right are: $x^{12}_2$ (which equals $x^{13}_3$), the intersection with $\inprod{v_2}{x}=1$, and the intersection with $\inprod{v_3}{x}=1$; and therefore from bottom left to bottom right are: the intersection with $\inprod{v_3}{x}=-1$, the intersection with $\inprod{v_2}{x}=-1$, and the intersection with $x^{12}_1$ (which equals $x^{13}_1$).
	\bo{Needs more justification why these points are always in this order (up to renaming of $v_2$ and $v_3$).}\jessie{Should we be able to take these to be in clockwise order WLOG in the grand scheme of trying to pack 5 normals into 180 degrees?  The order of the intersections follows from the clockwise order of the normals.  (ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)}

@@

	\bo{I'm not sure the below is a proof, because you could have linear combinations with any coefficients, so I don't think this proves that the only solutions are negating rows. I think we have to appeal to Mathematica from here on out.}
	\jessie{Yeah definitely.  I hadn't touched this since before yesterday.}
	In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
	(Note that any combination of row pairs works without loss of generality.)
	The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
	One can verify with mathematical software that $M_4$ has rank $2$ if it is in the following form:
	\[
	\begin{bmatrix}
	-1 & -1 & -1 & 1 & 1 & a \\
	1 & 1 & 1 & -1 & -1 & -a \\
	b & 1 & -1 & 1 & -1 & -1 \\
	-b & -1 & 1 & -1 & 1 & 1 \\
	\end{bmatrix}
	\] with $a, b \in [-1,1]$.
	Plugging in this solution set into the larger matrix yields
	\[
	\begin{bmatrix}
	{\color{red} -1} & {\color{red} -1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & {\color{red} a} & -1 & \cdot & \cdot & \cdot \\
	{\color{red} 1} & {\color{red} 1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & {\color{red} a} & \cdot & -1 & \cdot & \cdot \\
	{\color{red} b} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & \cdot & \cdot & -1 & \cdot \\
	{\color{red} -b} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & \cdot & \cdot & \cdot & -1 \\
	\cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & 1 & 1\\
	\end{bmatrix}
	\]

>>>>

	If we consider the four lines $\inprod{v_2}{x}=1, \inprod{v_2}{x}=-1, \inprod{v_3}{x}=1, \inprod{v_3}{x}=-1$, we therefore have three points of intersection with the line $\inprod{v_1}{x}=1$ and three with the line $\inprod{v_1}{x}=-1$. 
	WLOG, these points from top left to top right are: $x^{12}_2$ (which equals $x^{13}_3$), the intersection with $\inprod{v_2}{x}=1$, and the intersection with $\inprod{v_3}{x}=1$; and therefore from bottom left to bottom right are: the intersection with $\inprod{v_3}{x}=-1$, the intersection with $\inprod{v_2}{x}=-1$, and the intersection with $x^{12}_1$ (which equals $x^{13}_1$).
	\bo{Needs more justification why these points are always in this order (up to renaming of $v_2$ and $v_3$).}\jessie{Should we be able to take these to be in clockwise order WLOG in the grand scheme of trying to pack 5 normals into 180 degrees?  The order of the intersections follows from the clockwise order of the normals.  (ex: if the order was $v_2, v_1, v_3$, we would still get a contradiction, but in the first case like Figure~\ref{fig:intersection-graph-ex} I think)} \bo{I think yes, since we didn't assume anything including that $v_1$ had largest norm. We can discuss...}

@@

%	\bo{I'm not sure the below is a proof, because you could have linear combinations with any coefficients, so I don't think this proves that the only solutions are negating rows. I think we have to appeal to Mathematica from here on out.}
%	\jessie{Yeah definitely.  I hadn't touched this since before yesterday.}
%	In characterizing the solutions to the smaller matrix rank problem, let us establish the linear equality of the first two rows and second two rows.
%	(Note that any combination of row pairs works without loss of generality.)
%	The first column containing $[-1 \; 1]^T$ implies that we must have the two rows being the negation of each other, and similarly for the third and fourth rows with the final column.
        We have verified with Mathematica that $M_4$ has rank $2$ if and only if it is in the following form, up to a couple symmetries.
	\[
	\begin{bmatrix}
	-1 & -1 & -1 & 1 & 1 & a \\
	1 & 1 & 1 & -1 & -1 & -a \\
	b & 1 & -1 & 1 & -1 & -1 \\
	-b & -1 & 1 & -1 & 1 & 1 \\
	\end{bmatrix}
	\] with $a, b \in [-1,1]$.
	Plugging in this solution set into the larger matrix yields
	\[
        M_5' =
	\begin{bmatrix}
	{\color{red} -1} & {\color{red} -1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & {\color{red} a} & -1 & \cdot & \cdot & \cdot \\
	{\color{red} 1} & {\color{red} 1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & {\color{red} a} & \cdot & -1 & \cdot & \cdot \\
	{\color{red} b} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} -1} & \cdot & \cdot & -1 & \cdot \\
	{\color{red} -b} & {\color{red} -1} & {\color{red} 1} & {\color{red} -1} & {\color{red} 1} & {\color{red} 1} & \cdot & \cdot & \cdot & -1 \\
	\cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & 1 & 1\\
	\end{bmatrix}
	\]
        Again, using Mathematica, we have verified that $M_5'$ cannot be of rank $2$ (and repeated this for each symmetrical set of solutions to $M_4$).
